Review of Assigned Readings

### 2017-12-27 documentation/documentation.tex
add collectTwitterData.py

\subsubsection{API: Bitcoinaverage.com}
Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin. The following requests delivers data for an per hour monthly sliding window.
\paragraph{Request}\mbox{}\\
The request to get the data for an per hour monthly sliding window looks as follows. This request require authentication that requires registration and the generation of an API key. The registration and generation of an API key is freely available on bitcoinaverage.com. The collectCryptocurrencyData.py already contains the necessary keys. This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.  
\begin{lstlisting}[language=bash]
https://apiv2.bitcoinaverage.com/indices/global/history/BTCUSD?period=monthly&?format=json
\end{lstlisting}
\paragraph{Response}

>>>>

\subsubsection{API: Bitcoinaverage.com}
Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin. The following requests delivers data for an per hour monthly sliding window.
\paragraph{Request}\mbox{}\\
The request to get the data for an per hour monthly sliding window looks as follows. This request require authentication that requires registration and the generation of an API key. The registration and generation of an API key is freely available on bitcoinaverage.com. The collectCryptocurrencyData.py already contains the necessary keys. This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.  
\begin{lstlisting}[language=bash]
https://apiv2.bitcoinaverage.com/indices/global/history/BTCUSD?period=monthly&?format=json
\end{lstlisting}
\paragraph{Response}
An excerpt of an example response looks like the following:
\begin{lstlisting}
[
    {
        "high": 8271.04, 
        "average": 8247.83, 
        "open": 8242.39,
        "low": 8217.72, 
        "time": '2017-11-22 15:00:00'
    }, 
    {
        "high': 8246.82,
        "average": 8203.19,
        'open': 8203.81,
        'low': 8157.25,
        'time': '2017-11-22 14:00:00'
    }, 
    {
        'high': 8267.27, 
        "average": 8238.62, 
        'open': 8248.77, 
        'low': 8198.54, 
        'time': '2017-11-22 13:00:00'
    }
]
\end{lstlisting}
